Hippocampal segmentation with MAGeT

### 2012-11-22 paper.Rnw
Calculating r/p-values for ADNI/SZFEP plots, but display code currently commented out due to ugliness

\SweaveOpts{echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', tidy = FALSE, comment = NA, cache = TRUE}
<<loadpackages, results="hide", echo=FALSE, cache=FALSE>>=
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
@

@@

\begin{figure}[h]
<<ADNI-baseline-volumes-boxplot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-prep',cache=T>>=
qplot(DX,value,data=melt(totals,id.vars=c("ID","DX"),
      measure.vars=c("FSL","MAPER","MAGeT","SNT"),na.rm=T),
      colour=variable,geom="boxplot") + 
        xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")
@
  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-boxplot}
\end{figure}

\begin{figure}[h]
<<ADNI-baseline-volumes-plot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes',cache=T>>=
qplot(SNT,value,data=melt(totals,id.vars=c("ID","SNT"),
      measure.vars=c("FSL","MAPER","MAGeT")),
      colour=variable, geom="smooth", method="lm") + 
    geom_point() +
    xlab("Total Hippocampal Volume (Manual Segmentation)") + 
    ylab("Total Hippocampal Volume (Automatic Segmentation)")
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}

@@

\begin{figure}[h]
<<SZ_volumes,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes',cache=T>>=
SZ_volumes=read.csv("data/SZ_volumes_by_method.csv")
qplot(Manual,MAGeT,data=SZ_volumes) + geom_smooth(method="lm") + 
    xlab("Total Hippocampal Volume (Manual Segmentation)") + 
    ylab("Total Hippocampal Volume (MAGeT Segmentation)")

>>>>

\SweaveOpts{echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', tidy = FALSE, comment = NA, cache = TRUE}
<<loadpackages, results="hide", echo=FALSE, cache=FALSE>>=
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
options(digits=3)
@

@@

\begin{figure}[h]
<<ADNI-baseline-volumes-boxplot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-prep',cache=T>>=
qplot(DX,value,data=melt(totals,id.vars=c("ID","DX"),measure.vars=c("FSL","MAPER","MAGeT","SNT"),na.rm=T),
      colour=variable,geom="boxplot") + 
        xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")

@
  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-boxplot}
\end{figure}

\begin{figure}[h]
<<ADNI-baseline-volumes-plot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes',cache=T>>=
by_snt_volumes = melt(totals,id.vars=c("ID","SNT"), measure.vars=c("FSL","MAPER","MAGeT"))
fsl=subset(by_snt_volumes, variable=="FSL")
maper=subset(by_snt_volumes, variable=="MAPER")
maget=subset(by_snt_volumes, variable=="MAGeT")

qplot(SNT,value,data=by_snt_volumes,
      colour=variable, geom="smooth", method="lm") + 
    geom_point() +
#     geom_text(aes(
#       label=paste("FSL       R=", round(cor(fsl$SNT,fsl$value, use="complete.obs"), 2), 
#                   ", p<", round(as.double(t.test(fsl$SNT,fsl$value, paired=T)["p.value"]), 2)),
#       x=1800,y=10000, hjust=0,size=2)) + 
#     geom_text(aes(
#       label=paste("MAPER R=", round(cor(maper$SNT,maper$value, use="complete.obs"), 2), 
#                   ", p<", t.test(maper$SNT,maper$value, paired=T)["p.value"]), 
#       x=1800,y= 9500, hjust=0, size=2)) +
#     geom_text(aes(
#       label=paste("MAGeT  R=", round(cor(maget$SNT,maget$value, use="complete.obs"),2), 
#                   ", p<", t.test(maget$SNT,maget$value, paired=T)["p.value"]), 
#       x=1800,y= 9000, hjust=0, size=2)) +
    xlab("Total Hippocampal Volume (Manual Segmentation)") + 
    ylab("Total Hippocampal Volume (Automatic Segmentation)")
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}

@@

\begin{figure}[h]
<<SZ_volumes,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes',cache=T>>=
SZ_volumes=read.csv("data/SZ_volumes_by_method.csv")
qplot(Manual,MAGeT,data=SZ_volumes) + geom_smooth(method="lm") + 
#   geom_text(aes(
#       label=paste("R=", round(cor(Manual,MAGeT, use="complete.obs"), 2), 
#                   ", p<", t.test(Manual, MAGeT, paired=T)["p.value"]),
#       x=6500,y=10000, hjust=0,size=2)) +
    xlab("Total Hippocampal Volume (Manual Segmentation)") + 
    ylab("Total Hippocampal Volume (MAGeT Segmentation)")
